---
title: "Minimally Clinically Important Difference"
subtitle: "Review in Statistical ASpects"
author: "<strong>Boncho Ku, Ph.D. in Statistics</strong>"
institute: "<br/> Korea Institute of Oriental Medicine"
date: "<br> 2021/03/23 "
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, ../assets/css/footer.css, ../assets/css/metropolis-ak.css]
    # lib_dir: "../docs/libs"
    lib_dir: "libs"
    nature:
      highlightStyle: github
      titleSlideClass: [middle, left]
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

```{r setup-knitr, include=FALSE}
options(htmltools.dir.version = FALSE)
# knitr::opts_knit$set(root.dir='..')
knitr::opts_chunk$set(eval = TRUE, 
                      echo = FALSE, 
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      message=FALSE,
                      warning=FALSE, 
                      dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center", 
                      #fig.width = 7,
                      #fig.height = 7, 
                      fig.keep='all', fig.retina=3)

```


```{r setup-library}
library(tidyverse)
library(MASS)
library(reshape2)
library(plyr)
library(tidyverse)
library(lubridate)
library(readxl)
library(tidyselect)
library(tidystats)
library(glue)
library(here)
library(gt)
library(gtsummary)
library(kableExtra)

```



# `r emo::ji("wave")` Hello

### me: **Boncho Ku**

- **Statistician**, _Korea Institute of Oriental Medicine_
    + github: **@zorba78**
    + email: **secondmoon@kiom.re.kr**

- **Team**: Clinical Research Coordinating Team    


### Current Works in KIOM

.pull-left[
#### **Data Science**
- Statistical learning model
- Text mining
- Data linkage/statistical matching
- Data management
]


.pull-right[
#### **Biostatistics**
- Experiment & study design: RCT and observational study 
- Sample size calculation
- Statistical consulting and lecturing
]


### Slides: **https://zorba78.github.io/ust-medical-statistics**

---

class: inverse, center, middle

# Small reviews for Statistics 


---

# Statistical Significance


---


# Myth of P-value 



---

class: inverse, center, middle

# Minimally Clinically Important Difference


---

# Definition


---

# Anchor Methods



---

# Distribution-based Methods



---

# Delphi Methods


---

class: inverse, center, middle

# Applications




